Mass and occupation fraction of dark matter halos hosting Lyman-$\alpha$ emitters at $z\sim 3$

### 2014-01-03 paper/ms.tex
new paragraphs in the caveats sectionm, minor modifs in the conclusions

There are two important caveats for the work presented here. The first is the
assumption of a single LAE per dark matter halo. This contradicts the
general expectation of dark matter sub-halos in the simulation to host
satellite galaxies. However, it has been found in analysis based on
the shape of the correlation function \citep{Jose2013b} that satellite
galaxies are not a dominant population, making our initial
approximation a reasonable one. {\bf The lack of close pairs }Therefore we conclude that including
the effect of satellite galaxies does not change the main results
reported in this \documentname.

The second caveat are the precise values for the mass intervals. These
values are quoted from halos defined using a FOF halo
finder. Different halo finders and definitions for the detection
density threshold can yield different masses up to a factor $\sim 2$\citep{More2011}. For 
instance a Friends-of-Friends algorithm with linking length $l=0.20$
times the average inter-particle distance finds halos on average $1.4$
times less massive than halos defined  with an spherical overdensity
algorithm halos \citep{Bolshoi}. Therefore, the mass values for
$M_{\rm min}$ and $M_{\rm max}$ should not be considered exact within
less than $\sim 0.2$ dex.

{\bf Turning filter values into cosmological volumes.}

{\bf Comparing results for the clustering and the ACF from surveys with different EW cuts.}

@@

We find that {\bf the information for the number density constrains
  the minium mass to the range
  $10^{10}\hMsun < M_{\rm min} < 10^{11.5}\hMsun$ while the clustering
  constrains the upper mass $M_{\rm    max} < 10^{12}\hMsun$. However,
  this is insufficient to impose a tight constraint  on the escape
  fraction.} Furthermore, we find that the mass range defined as
$\Delta M=\log_{10}M_{\rm max} - \log_{10}M_{\rm min}$ is always
$\Delta M\leq 1.0$.

The wide range in values for the escape fraction is allowed by the
large dispersion in the statistics derived from the
mocks. This uncertainty is unexpected from previous studies that
unanimously favor low values for the occupation
fractions \citep[i.e.][]{Gawiser2007,Ouchi2010}. Nevertheless, all the
halo mass ranges and occupation fractions deduced previous analysis
are a subset of the models we find in this \documentname.

All of our preferred models support the notion that the most massive
halos at $z=3.1$ do not host detectable LAEs. The existence of a
narrow mass range for halos hosting LAEs, $\Delta  M\leq 1.0$ dex, has
two different explanations at least. The first is having LAEs with a
decreasing \ly escape fraction with increasing mass, the second is
having larger screening effects by neutral Hydrogen around the most
massive systems \citep{Laursen2009,ForeroRomero2011}.

@@

In summary, we show that {\bf the currently available spatial information of LAEs cannot
put a tight constraint on their occupation fraction of dark matter
halos}. This information can confidently be used to establish that
these galaxies are hosted in low mass halos with masses within a range
spanning less than a factor of ten. We foresee that the new
observations with new instruments (such as MUSE, Hyper SuprimeCam and
HETDEX) covering larger fields and a wider range of luminosities will
be key in reducing cosmic variance and imposing tighter constraints on
the properties of dark matter halos hosting LAEs. At the same time,
additional modeling for \ly radiation transfer is needed to put a
tighter constrain on the \ly escape fraction in high redshift
galaxies, also paying attention to newly framed physical phenomena,
such as the stochasticity \citep{ForeroRomero2013} in the star
formation process, which might play a role in inducing detection
biases in high redshift LAEs.

>>>>

There are four caveats for the work presented here that are important
to keep in mind. The first is the  
assumption of a single LAE per dark matter halo. This contradicts the
general expectation of dark matter sub-halos in the simulation to host
satellite galaxies. However, it has been found in analysis based on
the shape of the correlation function \citep{Jose2013b} that satellite
galaxies are not a dominant population, making our initial
approximation a reasonable one. {\bf The lack of close pairs in
  observations is another hint that the observed LAE population matches}
Therefore we conclude that including
the effect of satellite galaxies does not change the main results
reported in this \documentname.

The second caveat is the precise values for the mass intervals. These
values are quoted from halos defined using a FOF halo
finder. Different halo finders and definitions for the detection
density threshold can yield different masses up to a factor $\sim 2$\citep{More2011}. For 
instance a Friends-of-Friends algorithm with linking length $l=0.20$
times the average inter-particle distance finds halos on average $1.4$
times less massive than halos defined  with an spherical overdensity
algorithm halos \citep{Bolshoi}. Therefore, the mass values for
$M_{\rm min}$ and $M_{\rm max}$ should not be considered exact within
less than $\sim 0.2$ dex.

{\bf The third caveat is the exact value that was used to turn
  filter values into cosmological volumes. Strictly speaking the
  volume probed is a function of the \ly luminosity. Brighter LAEs
  probe a larger volume than fainter ones \citep{Gronwall07}. A proper
way to account for this effect would require to assign luminosities to
each mock LAE and process them in a similar way as mock
observations. However, we can estimate that under the considerations
presented in \citep{Gronwall07}, one could expect the survey depth to
change at most by a factor of $\sim2$. Considering the dependence
of the number density on halo mass (right panel of Figure 1), such
change in volume could be compensated by different values for the
favored model parameters $M_{\rm  min}$ and $M_{\rm max}$ by about the
same factor of $\sim2$. }

{\bf A fourth caveat is the comparing results for the number density
  statistics and the ACF from surveys with different EW cuts. In this
  sense we highlight againt that the two filters and selection
  criteria used by \citep{Ouchi2008} and \citep{Yamada2012} are only
  slightly different. The number densities in the general fields by
  \citep{Yamada2012} is $0.083\pm0.004$ arcmin$^{-2}$, while in
  \citep{Ouchi2008} is $0.099\pm0.005$ arcmin$^{-2}$. This gives us
  confidence that the two different samples can give a self-consistent
  picture for our studies.}

@@

{\bf We find that the information for the number density constrains
  the minium mass to the range
  $10^{10}\hMsun < M_{\rm min} < 10^{11.5}\hMsun$ while the clustering
  constrains the upper mass $M_{\rm    max} < 10^{12}\hMsun$. However,
  this is insufficient to impose a tight constraint  on the escape
  fraction.} Furthermore, we find that the mass range defined as
$\Delta M=\log_{10}M_{\rm max} - \log_{10}M_{\rm min}$ is always
$\Delta M\leq 1.0$.

{\bf Our approach has allowed the discovery of possible models that have
been overloooked so far in the literature. A central role in these new
models is played by the wide range of escape fraction values. A wide
range in the escape fraction is unexpected from previous studies that
unanimously favor low values for the occupation
fractions \citep[i.e.][]{Gawiser2007,Ouchi2010}. The larges
innnovation in our analysis is the construction of mock obsevations
that directly explore the impact of cosmic variance, which seems to be
at the root of the large uncertainties in the escape fraction.}

Nevertheless, all the halo mass ranges deduced previous analysis are a
subset of the models we find in this \documentname.  All of our
preferred models support the notion that the most massive halos at
$z=3.1$ do not host detectable LAEs. The existence of a narrow mass
range for halos hosting LAEs, $\Delta  M\leq 1.0$ dex, has two
different explanations at least. The first is having LAEs with a
decreasing \ly escape fraction with increasing mass, the second is
having larger screening effects by neutral Hydrogen around the most
massive systems \citep{Laursen2009,ForeroRomero2011}.

@@

In summary, we show that {\bf the currently available spatial
  information of LAEs cannot put a tight constraint on their
  occupation fraction of dark matter halos}. This information can
confidently be used to establish that these galaxies are hosted in low
mass halos with masses within a range spanning less than a factor of
ten. {\bf From the point of view of Dark Energy surveys such as
  HETDEX, the narrow mass range for LAEs can be seen as an advantage,
  due to its simplicity, for their modeling aiming at recovering
  cosmological parameters.} We foresee that the new observations with
new instruments (such as MUSE, Hyper SuprimeCam and HETDEX) covering
larger fields and a wider range of luminosities will be key in reducing cosmic variance and imposing tighter constraints on
the properties of dark matter halos hosting LAEs. At the same time,
additional modeling for \ly radiation transfer is needed to put a
tighter constrain on the \ly escape fraction in high redshift
galaxies, also paying attention to newly framed physical phenomena,
such as the stochasticity \citep{ForeroRomero2013} in the star
formation process, which might play a role in inducing detection
biases in high redshift LAEs.
